Simple connectome inference from partial\\[1ex] correlation statistics in calcium imaging

### 2014-11-06 oral/slides.tex
several changes

\title{Simple connectome inference from partial\\[1ex]
correlation statistics in calcium imaging}
\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ernst and Pierre Geurts.}}
\date{}

@@

From {\color{i6blue} time-series of the neuron activity}, the \textbf{goal} is to {\color{red} \textbf{infer} the directed connections between neurons}.

\note{

	Before the main part of this presentation, I would like to mention that we are not biologist and we are not expert of the connectome inference. We see the challenge as an inference problem and maybe in a naive point of view for some points.

}

@@

\textbf{Advantages and drawbacks}:
\begin{itemize}
\item[{\color{green} \cmark}] Only direct associations
\item[{\color{green} \cmark}] Filter out spurious indirect effects
\item[{\color{green} \cmark}] Symmetric 
\item[{\color{green} \cmark}] Easy to compute \\ (with lots of data) \\[2ex]
\item[{\color{red} \xmark}] Edge orientation
\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
\end{itemize}

@@

\begin{center}
\textit{Average scores on normal-{1,2,3,4} datasets.
}
\includegraphics[width=8cm]{images/data_stage.png}
\end{center}

@@

\begin{center}
\textit{Average scores on normal-{1,2,3,4} datasets.
}
\includegraphics[width=9cm]{images/data_method.png}
\end{center}
% \begin{table}[t]

>>>>

\title{Simple connectome inference from partial\\[1ex]
correlation statistics in calcium imaging}
\author{{\small Antonio Sutera, Arnaud Joly, Vincent François-Lavet, Zixiao Aaron Qiu\\[1ex] Gilles Louppe, Damien Ernst and Pierre Geurts (aka The AAAGV Team).}}
\date{}

@@

\vspace{2cm}

From {\color{i6blue} time-series of the neuron activity}, the \textbf{goal} is to {\color{red} \textbf{infer} the directed connections between neurons}.\\[5ex]

\begin{center}
\includegraphics[width=7cm]{images/network_2.pdf}
\end{center}

@@

\textbf{Advantages and drawbacks}:
\begin{itemize}
\item[{\color{green} \cmark}] Only direct associations
\item[{\color{green} \cmark}] Filter out spurious indirect effects
% \item[{\color{green} \cmark}] Symmetric 
\item[{\color{green} \cmark}] Easy to compute \\ (with lots of data) \\[2ex]
\item[{\color{red} \xmark}] Edge orientation
\item[{\color{red} \xmark}] Sensitive to the value of parameters in the filtering process
\end{itemize}

@@

\begin{center}
\textit{Average scores on normal-{1,2,3,4} datasets.
}
\includegraphics[width=8.5cm]{images/data_stage.png}
\end{center}

@@

\begin{center}
\textit{Average scores on normal-{1,2,3,4} datasets.
}
\includegraphics[width=10cm]{images/data_method.png}
\end{center}
% \begin{table}[t]
